---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r, setup, include = FALSE}
library(gt)
library(stringr)
library(dplyr)
```

# femicides_fr

<!-- badges: start -->
![last-update](https://img.shields.io/static/v1?label=last update&message=`r lubridate::today()`&color=2aac48&labelColor=252a2f)
![workflow-update](https://github.com/cedricbatailler/femicides_fr/actions/workflows/femicide-tweets.yml/badge.svg)
<!-- badges: end -->

A data set of femicides in France as reported by [\@feminicidesfr](https://twitter.com/feminicidesfr/).

### How does it work?

[\@feminicidesfr](https://twitter.com/feminicidesfr/) is a Twitter account
conducting a census of the femicides reported in the press, in France. The
account is managed by a feminist group composed of volunteers.

Every day, at midnight, [a `R`
script](https://github.com/cedricbatailler/femicides_fr/blob/main/R/update.R)
looks for the most recent tweets from
[\@feminicidesfr](https://twitter.com/feminicidesfr/) which my contains new
femicide reports. If found, the new reports are added to the [data
set](https://github.com/cedricbatailler/femicides_fr/blob/main/data/femicide.csv).

### Quickstart

If you want to open the data set in a Google Sheet document, just open [a new
Google Sheet document](https://sheets.new) and paste the following in the first
cell.

`=importData("https://github.com/cedricbatailler/femicides_fr/raw/main/data/femicide.csv")`

Or, you can manually download the data set
[here](https://github.com/cedricbatailler/femicides_fr/blob/main/data/femicide.csv).

### Last tweets

```{r echo=FALSE, message=FALSE}
readr::read_csv("data/femicide.csv", 
                col_types = "c??????") %>% 
  mutate(tweet_id = glue::glue("[{str_trunc(tweet_id, width = 10)}](https://twitter.com/feminicidesfr/status/{tweet_id})"),
         tweet_text = str_trunc(tweet_text, width = 30),
         tweet_urls = str_trunc(tweet_urls, 20)) %>% 
  arrange(desc(tweet_datetime)) %>%  
  select(tweet_id, tweet_datetime, tweet_text, year, femicide) %>% 
  head(5) %>% 
  gt() %>% 
  fmt_markdown(tweet_id) %>% 
  tab_source_note("Source @feminicidesfr") %>% 
  as_raw_html(inline_css = TRUE)

```

## Similar projects

-   [2021 - Féminicides par Compagnons ou Ex - Google My Maps](https://www.google.com/maps/d/viewer?mid=1AoTHJTAvWz-P1ddCKe1NhWtdsOQgcLPA): An interactive map of femicide maintained by [\@feminicidesfr](https://twitter.com/feminicidesfr/).

## Code of conduct

Please note that this project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
